Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-24 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:24	13:46:50	(Thu24.Sep)

\begin{figure}[tbp]%
\includegraphics[width=\linewidth]{gfx/cross_tagged.png}%
\caption{One of the objects used to test the beamformers is a 1\,m long cross attached to an anchor with a diameter of 13\,cm.}\label{cross}
\end{figure}

@@

Since LCA operates with the same optimization criterion, we will be using approximately a factor 8 lateral oversampling for both beamformers. The images appear more visually pleasing and detailed up to 8, but we consider an absolute minimum to be 2. In \mediaII{} we demonstrate this with LCA images changing as a function of a lateral oversampling factor. The displayed images are all upinterpolated to the same size, but the detail level varies. 
% 
% \todo{Need $M$ in the image sector. Why???}

\todo{
- Abs -> adds a factor 2\\
- log -> infinity?\\
- near field -> range and azimuth is coupled}

@@

Observe from \Fig{mvdr_selected_windows} that MVDR seems prefers symmetric window responses, even if it is free to choose non-symmetric ones. The symmetry is most predominant in shadow and speckle regions, while in highlight the windows are approximately symmetric within the illuminated\todo{valid term?} sector of the seafloor. We have observed this symmetry to be a side-effect of the averaging steps needed to build the sample covariance matrix, which is key to allow  MVDR to run in near snapshot mode in an active system. The peak sidelobe levels of the MVDR windows they are mostly between -13\,dB and -43\,dB. This corresponds to that of the rectangular and Hamming window, or a Kaiser window with $\beta=0$ and $\beta=2$, respectively.

@@

The images in \Fig{oversampling_mosaic_bounds} much improved sidelobe suppression with a an upper for bound for $\beta$ of 2, but it improved further as this bound was adjusted up to 5. No noticeable difference were observed for higher values than 5. The images also demonstrate that increasing the steering $\phi$ improves the resolution of the strong scatterers. For this sonar the Rayleigh resolution is $\Delta=0.0125$ radians (0.72$^\circ$), thus a point scatterer imaged at 19\,m with a rectangular DAS would have a lateral FWHM of $0.125\cdot19\,\text{m}\cdot0.89=21\,\text{cm}$. This is close to the FWHM of the anchor in the DAS image in \Fig{oversampling_mosaic_bounds}. As we increase steering to either 50\% or 100\% of the -3dB width, the FWHM drops to 73\% or 53\% to that of the rectangular window, respectively.

>>>>

\begin{figure}[tbp]%
\includegraphics[width=\linewidth]{gfx/cross_tagged.png}%
\caption{One of the objects used to test the beamformers is a 1\,m long cross attached to an anchor with a diameter of $\approx$13\,cm.}\label{cross}
\end{figure}

@@

Since LCA operates with the same optimization criterion, we will be using approximately a factor 8 lateral oversampling for both beamformers. The images appear more visually pleasing and detailed up to 8. We consider an absolute minimum to be 2, due to the non-linear nature of delaying pixels that isn't strictly in the far field, and of displaying the absolute value of the pixels on a decibel scale. In \mediaII{} we visualize the effect of changing the lateral oversampling factor on a set of LCA images. The displayed images are all upinterpolated to the same size, but the detail level varies. 
% 
% \todo{Need $M$ in the image sector. Why???}

@@

Observe from \Fig{mvdr_selected_windows} that MVDR seems prefers symmetric window responses, even if it is free to choose non-symmetric ones. The symmetry is most predominant in shadow and speckle regions, while in highlight the windows are approximately symmetric within the illuminated sector of the seafloor. We have observed this symmetry to be a side-effect of the averaging steps needed to build the sample covariance matrix, which is key to allow  MVDR to run in near snapshot mode in an active system. The peak sidelobe levels of the MVDR windows they are mostly between -13\,dB and -43\,dB. This corresponds to that of the rectangular and Hamming window, or a Kaiser window with $\beta=0$ and $\beta=2$, respectively.

@@

The images in \Fig{oversampling_mosaic_bounds} much improved sidelobe suppression with a an upper for bound for $\beta$ of 2, but it improved further as this bound was adjusted up to 5. No noticeable difference were observed for higher values than 5. The images also demonstrate that increasing the steering $\phi$ improves the resolution of the strong scatterers. For this sonar the Rayleigh resolution is $\Delta=0.0125$ radians (0.72$^\circ$), thus a point scatterer imaged at 19\,m with a rectangular DAS would have a lateral FWHM of $0.125\cdot19\,\text{m}\cdot0.89=21\,\text{cm}$. This is close to the FWHM of the anchor in the DAS image in \Fig{oversampling_mosaic_bounds}, which means that the acoustic fingerprint of the anchor is similar to a point source. This suggests the anchor reflections to be specular and that we view its rounded side. As we increase steering to either 50\% or 100\% of the -3dB width, the FWHM drops to 73\% or 53\% to that of the rectangular window, respectively.
